msre reactor design

### 2022-07-01 core/docs/msrecore.tex
typo

care is taken to give proper references to the original data, figure, tables, etc. likewise, any quantity or feature laking documentation or reference not yet found will be estimated or extrapolated from the available information.

@@

\section{\emph{core vessel}}
\subsection{\emph{lower and upper vessel plenum}}
\textcite[page 14]{ornl-tm-3229} states about the lower vessel plenum:
\enquote{\textit{the lower plenum of the core vessel is formed by a standard 60 in. od asme flanged and dished head}} and \textcite[page 25]{ornl-tm-3229} states about the upper vessel plenum:
\enquote{\textit{the reactor vessel upper plenum is similar to the lower plenum in that it is forme from a standard asme flanged and dished head}}.

>>>>

care is taken to give proper references to the original data, figures, tables, etc. likewise, any quantity or feature lacking documentation or reference not yet found will be estimated or extrapolated from the available information.

@@

\section{\emph{core vessel}}
\subsection{\emph{lower and upper vessel plenum}}
\textcite[page 14]{ornl-tm-3229} states about the lower vessel plenum:
\enquote{\textit{the lower plenum of the core vessel is formed by a standard 60 in. od asme flanged and dished head}} and \textcite[page 25]{ornl-tm-3229} states about the upper vessel plenum:
\enquote{\textit{the reactor vessel upper plenum is similar to the lower plenum in that it is formed from a standard asme flanged and dished head}}.
